---
title: "Healthcare Intel Digest"
format:
  html:
    toc: true
    toc-depth: 4
    embed-resources: true
  gfm:
    toc: false
params:
  report_path: "inputs/current_report.md"
execute:
  echo: false
  warning: false
  message: false
---

```{r}
source("weekly_report.R")
result <- prepare_report(params$report_path)
report <- result$report
facts <- result$company_facts
html_output <- knitr::is_html_output()

# Companies with their own subsection, so other sections can link a name straight
# to it. A name that has no overview stays plain text rather than a dead link.
overview_tickers <- vapply(result$overviews, function(item) item$ticker, character(1))
company_link <- function(name, ticker) {
  if (!length(ticker) || is.na(ticker) || !(ticker %in% overview_tickers)) return(name)
  if (html_output) sprintf("<a href=\"#%s\">%s</a>", report_anchor(ticker), name)
  else sprintf("[%s](#%s)", name, report_anchor(ticker))
}
# The table of contents lists the report's sections plus the strategy brief's own
# structure. Every other subsection is marked `.unlisted` so a reader scanning the
# contents sees the report's shape rather than every company and category name.
# The attribute is HTML-only; Markdown has no heading attributes.
sub_heading <- function(text) {
  if (html_output) paste0("### ", text, " {.unlisted}\n\n") else paste0("### ", text, "\n\n")
}
fact <- function(ticker, column) {
  value <- facts[[column]][match(ticker, facts$ticker)]
  if (!length(value)) NA else value
}
```

```{r, results='asis'}
# HTML renders the YAML title as its own block; Markdown does not, so the heading is
# added there only. Emitting both is what printed the title twice.
if (html_output) cat(report_table_assets()) else cat("# ", rmarkdown::metadata$title, "\n\n", sep = "")
```

**Report date:** `r report$report_date`

`r report$body`

## Strategy Narrative

```{r, results='asis'}
narrative <- result$strategy_narrative
if (is.null(narrative)) {
  cat("No strategy narrative has been saved. Run `refresh_strategy_narrative()`.\n\n")
} else {
  # The source is a shared-conversation snapshot that does not update itself, so the
  # period it covers is stated here rather than assumed to be current.
  label <- if (is.na(narrative$period)) "period not stated" else paste("week of", narrative$period)
  fetched <- if (is.na(narrative$fetched_at)) "unknown" else substr(narrative$fetched_at, 1, 10)
  cat("*Strategy brief for the ", label, ", retrieved ", fetched, ".*\n\n", sep = "")
  cat(narrative$body, "\n\n", sep = "")
}
```

## Notable Changes

```{r, results='asis'}
if (is.null(result$previous_date)) {
  cat("No earlier final report is available; this report establishes the baseline.\n\n")
} else {
  cat("Price change from ", format(result$previous_date), " to ", format(report$report_date),
      ".\n\n", sep = "")
}
```

```{r, results='asis'}
moves <- result$weekly_moves
if (!is.null(result$previous_date) && nrow(moves)) {
  categories <- dplyr::filter(moves, type == "category") |>
    dplyr::arrange(dplyr::desc(price_move))
  if (nrow(categories)) {
    cat("**Category change, market-cap weighted**\n\n")
    report_table(
      tibble::tibble(Category = categories$name, Change = format_return(categories$price_move)),
      fills = list(Change = categories$price_move),
      sort_values = list(Change = categories$price_move)
    )
  }
}
```

```{r, results='asis'}
stock_moves <- dplyr::filter(moves, type == "stock", !is.na(price_move)) |>
  dplyr::distinct(ticker, name, price_move)
if (!is.null(result$previous_date) && nrow(stock_moves)) {
  shown <- result$movers_shown
  # Direction follows the sign of the move, not the row's position in the ranking:
  # taking the head and tail of a list would label an unchanged company "Declined".
  gained <- dplyr::filter(stock_moves, price_move > 0) |>
    dplyr::arrange(dplyr::desc(price_move)) |>
    utils::head(shown) |>
    dplyr::mutate(Direction = "Gained")
  declined <- dplyr::filter(stock_moves, price_move < 0) |>
    dplyr::arrange(price_move) |>
    utils::head(shown) |>
    dplyr::mutate(Direction = "Declined")
  table <- dplyr::bind_rows(gained, declined)
  if (!nrow(table)) {
    cat("No company price changed since the previous report.\n\n")
  } else {
    cat("**Largest company moves**\n\n")
    report_table(
      tibble::tibble(
        Direction = table$Direction,
        Company = purrr::map2_chr(table$name, table$ticker, company_link),
        Ticker = table$ticker, Change = format_return(table$price_move)
      ),
      fills = list(Change = table$price_move),
      sort_values = list(Change = table$price_move)
    )
  }
}
```

```{r, results='asis'}
if (!nrow(result$changes)) {
  cat("No configured performance changes were identified.\n\n")
} else {
  cat("**Rank and return changes**\n\n")
  for (detail in result$changes$detail) cat("- ", detail, "\n", sep = "")
  cat("\n")
}
```

## Category performance

```{r, results='asis'}
categories <- result$categories
report_table(
  tibble::tibble(
    Category = categories$category,
    Companies = categories$company_count,
    `Market cap` = format_market_cap(categories$market_cap),
    `3m Return` = format_return(categories$price_return_3m),
    `12m Return` = format_return(categories$price_return_12m),
    `24m Return` = format_return(categories$price_return_24m)
  ),
  fills = list(
    `3m Return` = categories$price_return_3m,
    `12m Return` = categories$price_return_12m,
    `24m Return` = categories$price_return_24m
  ),
  sort_values = list(
    Companies = categories$company_count,
    `Market cap` = categories$market_cap,
    `3m Return` = categories$price_return_3m,
    `12m Return` = categories$price_return_12m,
    `24m Return` = categories$price_return_24m
  )
)
```

Category returns use the most recently saved market capitalizations as weights.

## Stock performance vs. SPY

Each chart shows the three strongest performers over its own window and the three
largest companies by market capitalization, drawn from the stocks selected for a deep
dive, against SPY. Prices are indexed to 100 at a shared date so companies with
different share prices can be compared directly. Every other selected stock is listed
beneath the chart with its change over the same period.

```{r}
market_caps <- dplyr::select(facts, ticker, market_cap)
selection_24 <- chart_series(result$price_performance, 24, market_caps)
selection_6 <- chart_series(result$price_performance, 6, market_caps)
# Companies that share a chart come first, so they take the best-separated slots;
# companies that only ever appear alone on their own overview chart follow. Built
# once and subset per chart, so a company's colour never depends on which other
# companies happen to share its chart.
charted_together <- sort(unique(c(selection_24$plotted, selection_6$plotted)))
chart_colors <- series_colors(
  c(facts$ticker, "SPY"),
  universe = c(charted_together, sort(setdiff(facts$ticker, charted_together)))
)
```

```{r, fig.width=9, fig.height=5.2}
if (!length(selection_24$plotted)) {
  cat("No saved price history is available for the selected stocks.\n")
} else {
  local({
    old_par <- graphics::par(mar = c(3.2, 3.6, 2.4, 0.6), mgp = c(2.2, 0.6, 0))
    on.exit(graphics::par(old_par), add = TRUE)
    plot_indexed_performance(
      result$price_performance, 24, selection_24$plotted,
      selection_24$returns, title = "Last 24 months", colors = chart_colors
    )
  })
}
```

```{r, results='asis'}
others <- selection_24$others
if (nrow(others)) {
  cat("Also selected, not shown above: ",
      paste0(others$ticker, " ", format_return(others$window_return), collapse = ", "),
      ".\n\n", sep = "")
}
```

```{r, fig.width=9, fig.height=5.2}
if (length(selection_6$plotted)) {
  local({
    old_par <- graphics::par(mar = c(3.2, 3.6, 2.4, 0.6), mgp = c(2.2, 0.6, 0))
    on.exit(graphics::par(old_par), add = TRUE)
    plot_indexed_performance(
      result$price_performance, 6, selection_6$plotted,
      selection_6$returns, title = "Last 6 months", colors = chart_colors
    )
  })
}
```

```{r, results='asis'}
others <- selection_6$others
if (nrow(others)) {
  cat("Also selected, not shown above: ",
      paste0(others$ticker, " ", format_return(others$window_return), collapse = ", "),
      ".\n\n", sep = "")
}
```

## Current top stocks

```{r, results='asis'}
for (horizon in return_horizons()) {
  cat(sub_heading(paste("Last", horizon, "Months")))
  table <- result$top_stocks |>
    dplyr::filter(horizon_months == horizon) |>
    dplyr::arrange(overall_rank)
  if (!nrow(table)) {
    cat("No ranked returns are available for this period.\n\n")
    next
  }
  report_table(
    tibble::tibble(
      Rank = table$overall_rank,
      Company = purrr::map2_chr(table$name, table$ticker, company_link),
      Ticker = table$ticker,
      `Market cap` = format_market_cap(table$market_cap),
      Return = format_return(table$price_return)
    ),
    fills = list(Return = table$price_return),
    sort_values = list(
      Rank = table$overall_rank, `Market cap` = table$market_cap, Return = table$price_return
    )
  )
}
```

## Companies by category

```{r, results='asis'}
category_returns <- result$categories
for (category_name in report$categories) {
  weighted <- category_returns$price_return_3m[match(category_name, category_returns$category)]
  heading <- paste0(category_name, " ", format_return(weighted))
  if (html_output && !is.na(weighted)) {
    # The subsector's own return is coloured on the same scale as the categories
    # table, so the heading says how this group compares without a second lookup.
    fill <- return_fills(category_returns$price_return_3m)[
      match(category_name, category_returns$category)
    ]
    heading <- sprintf(
      "%s <span style=\"background:%s;color:%s;padding:0.1rem 0.4rem;border-radius:4px;font-size:0.85em\">%s</span>",
      category_name, fill, contrast_ink(fill), format_return(weighted)
    )
  }
  cat(sub_heading(heading))
  table <- dplyr::filter(result$stocks, category == category_name)
  if (!nrow(table)) {
    cat("No companies are assigned to this category.\n\n")
    next
  }
  report_table(
    tibble::tibble(
      Company = purrr::map2_chr(table$name, table$ticker, company_link),
      Ticker = table$ticker,
      `Market cap` = format_market_cap(table$market_cap),
      `3m Return` = format_return(table$price_return_3m),
      `12m Return` = format_return(table$price_return_12m),
      `24m Return` = format_return(table$price_return_24m)
    ),
    fills = list(
      `3m Return` = table$price_return_3m,
      `12m Return` = table$price_return_12m,
      `24m Return` = table$price_return_24m
    ),
    sort_values = list(
      `Market cap` = table$market_cap,
      `3m Return` = table$price_return_3m,
      `12m Return` = table$price_return_12m,
      `24m Return` = table$price_return_24m
    )
  )
}
```

The percentage beside each category is its market-cap-weighted 3-month return.

## Upcoming earnings

```{r, results='asis'}
upcoming <- result$upcoming_earnings
if (!nrow(upcoming)) {
  cat("No saved earnings dates fall within the next seven days.\n\n")
} else {
  upcoming <- upcoming |>
    dplyr::mutate(
      category = dplyr::coalesce(fact(ticker, "category"), "Uncategorised"),
      market_cap = fact(ticker, "market_cap"),
      return_3m = fact(ticker, "price_return_3m"),
      return_12m = fact(ticker, "price_return_12m")
    )
  for (category_name in unique(upcoming$category[order(-dplyr::coalesce(upcoming$market_cap, -Inf))])) {
    table <- dplyr::filter(upcoming, category == category_name) |>
      dplyr::arrange(dplyr::desc(market_cap))
    cat(sub_heading(category_name))
    report_table(
      tibble::tibble(
        Company = purrr::map2_chr(table$name, table$ticker, company_link),
        Ticker = table$ticker,
        Date = format(table$next_earnings_date),
        `Market cap` = format_market_cap(table$market_cap),
        `3m Return` = format_return(table$return_3m),
        `12m Return` = format_return(table$return_12m)
      ),
      fills = list(`3m Return` = table$return_3m, `12m Return` = table$return_12m),
      sort_values = list(
        Date = as.numeric(table$next_earnings_date), `Market cap` = table$market_cap,
        `3m Return` = table$return_3m, `12m Return` = table$return_12m
      )
    )
  }
}
```

## Selected earnings highlights

```{r, results='asis'}
if (!length(result$earnings_summaries)) cat("No earnings summaries were selected.\n\n")
for (item in result$earnings_summaries) {
  name <- fact(item$ticker, "name")
  if (is.na(name)) name <- item$ticker
  cat(sub_heading(paste0(company_link(name, item$ticker), " (", item$ticker, ")")))
  cat(
    "*", fact(item$ticker, "category"), " · ", format_market_cap(fact(item$ticker, "market_cap")),
    " · 3m ", format_return(fact(item$ticker, "price_return_3m")),
    " · 12m ", format_return(fact(item$ticker, "price_return_12m")), "*\n\n", sep = ""
  )
  if (is.na(item$summary)) cat(item$message, "\n\n") else {
    cat("**Reported:** ", format(item$report_date), "\n\n", item$summary, "\n\n", sep = "")
    if (!is.na(item$source_url)) cat("[Google Finance source](", item$source_url, ")\n\n", sep = "")
  }
}
```

## Selected news

```{r, results='asis'}
if (!length(result$news)) cat("No company news was selected.\n\n")
without_news <- character()
for (item in result$news) {
  if (!nrow(item$articles)) {
    without_news <- c(without_news, item$ticker)
    next
  }
  cat(sub_heading(paste0(company_link(item$name, item$ticker), " (", item$ticker, ")")))
  for (index in seq_len(nrow(item$articles))) {
    article_date <- if (is.na(item$articles$published_date[[index]])) {
      paste0("first seen ", item$articles$first_seen_date[[index]])
    } else {
      as.character(item$articles$published_date[[index]])
    }
    cat("- [", item$articles$title[[index]], "](", item$articles$url[[index]], ") — ",
        item$articles$publisher[[index]], ", ", article_date, "\n", sep = "")
  }
  cat("\n")
}
if (length(without_news)) {
  cat("*Companies selected but no news available: ", paste(without_news, collapse = ", "), ".*\n\n", sep = "")
}
```

## Company overviews

```{r, results='asis', fig.width=7, fig.height=2.6}
if (!length(result$overviews)) cat("No company overviews were selected.\n\n")
for (item in result$overviews) {
  # An inline HTML anchor in both formats: Markdown's `{#id}` heading attribute is
  # not part of GitHub-flavoured Markdown, so pandoc dropped it and left every
  # company link in the Markdown copy pointing at nothing.
  cat(sub_heading(sprintf(
    "<a id=\"%s\"></a>%s (%s)", report_anchor(item$ticker), item$name, item$ticker
  )))
  cat(
    "*", item$category %||% "Uncategorised", " · ", format_market_cap(item$market_cap),
    " · 3m ", format_return(fact(item$ticker, "price_return_3m")),
    " · 12m ", format_return(fact(item$ticker, "price_return_12m")),
    " · 24m ", format_return(fact(item$ticker, "price_return_24m")), "*\n\n", sep = ""
  )
  chart <- performance_chart_data(item$ticker, report$report_date, horizons = 24L)
  if (nrow(chart)) {
    local({
      old_par <- graphics::par(mar = c(2.6, 3.4, 1.2, 0.6), mgp = c(2.1, 0.5, 0))
      on.exit(graphics::par(old_par), add = TRUE)
      plot_indexed_performance(
        chart, 24, unique(chart$ticker), colors = chart_colors
      )
    })
  }
  if (!is.na(item$description) && nzchar(item$description)) cat(item$description, "\n\n")
  if (!is.na(item$provider_description) && nzchar(item$provider_description)) {
    cat(item$provider_description, "\n\n")
  }
}
```

```{r, results='asis'}
# Data coverage and collection warnings are working notes: useful when reviewing a
# draft, noise in the version that gets circulated. They render in the Markdown
# output only.
coverage <- result$coverage
issues <- result$data_issues
recent_listings <- if (is.null(coverage)) NULL else dplyr::filter(coverage, expected_short)
short_history <- if (is.null(coverage)) character() else unexplained_short_history(coverage)
shifted_base <- if (is.null(coverage)) NULL else dplyr::filter(coverage, covers, days_late > 0)
lines <- character()

if (!is.null(issues) && nrow(issues)) {
  lines <- c(lines, paste0("- **", issues$issue, "** — ", issues$subject, ". ", issues$detail))
}
if (length(short_history)) {
  lines <- c(lines, paste0(
    "- Saved history cannot support a ", max(coverage$horizon_months), "-month return for ",
    paste(short_history, collapse = ", "), ". That horizon is blank for them; shorter horizons are unaffected."
  ))
}
if (!is.null(recent_listings) && nrow(recent_listings)) {
  lines <- c(lines, paste0(
    "- Listed less than ", max(coverage$horizon_months), " months ago, so that horizon is blank by nature: ",
    paste0(recent_listings$ticker, " (listed ", format(recent_listings$listed_on), ")", collapse = ", "), "."
  ))
}
if (!is.null(shifted_base) && nrow(shifted_base)) {
  lines <- c(lines, paste0(
    "- Measured from the earliest saved bar rather than the exact window edge, up to ",
    max(shifted_base$days_late), " day(s) later: ", paste(shifted_base$ticker, collapse = ", "), "."
  ))
}
if (!html_output && length(lines)) {
  cat("## Data coverage\n\n")
  cat("Everything below is reported rather than blocking: the report is produced from the data that is available.\n\n")
  cat(paste(lines, collapse = "\n"), "\n\n", sep = "")
}

warnings <- result$scraper_warnings
if (!html_output && isTRUE(result$show_scraper_warnings) && !is.null(warnings) && nrow(warnings)) {
  labels <- c(
    google_earnings = "Google Finance earnings", google_news = "Google Finance news",
    exchange = "Exchange lookup"
  )
  cat("## Data collection warnings\n\n")
  cat("The following Google Finance scrapes did not succeed on their most recent run. ",
      "`fallback` means the article came from the Massive news API instead. ",
      "The report used saved or fallback data where available; check the selectors if this persists.\n\n", sep = "")
  for (index in seq_len(nrow(warnings))) {
    source_label <- labels[[warnings$source[[index]]]] %||% warnings$source[[index]]
    detail <- if (is.na(warnings$detail[[index]])) "" else paste0(" — ", warnings$detail[[index]])
    cat("- **", warnings$ticker[[index]], "** (", source_label, ", ",
        warnings$status[[index]], ", last checked ",
        warnings$checked_at[[index]], ")", detail, "\n", sep = "")
  }
  cat("\n")
}
```

## Methodology

- Returns are split-adjusted price returns for the 3-, 12-, and 24-month periods ending on the report date.
- A return is blank when saved price history does not reach back through its horizon. The provider holds about two years of history from the current date, so on a new cache the 24-month base bar can fall a few days inside the window; a base bar up to `price_base_tolerance_days` late is used rather than blanking the return.
- Chart series are indexed to 100 at one shared date, so lines with different history lengths share an origin. Changes beside each series label are measured over that chart's own window.
- Category returns are market-cap-weighted averages of company returns; raw share prices are not averaged.
- Rankings are calculated independently for each horizon.
- Return colours run blue for gains and red for losses, calibrated within each column against the largest absolute move in it. Blue and red rather than green and red so the scale stays readable with colour-vision deficiency; every cell also shows its number.
- Notable changes compare with the latest earlier final report.
- Rendering reads saved local files and makes no external requests.
