---
title: "Healthcare Intel Digest"
format:
  html:
    toc: true
    toc-depth: 4
    embed-resources: true
    # Declaring a second format makes Quarto offer a download link to it in the
    # sidebar ("Other Formats"). The Markdown copy is archived beside the HTML, so
    # the link is noise in the contents.
    format-links: false
  gfm:
    toc: false
params:
  report_path: "inputs/current_report.md"
execute:
  echo: false
  warning: false
  message: false
---

```{r}
source("weekly_report.R")
result <- prepare_report(params$report_path)
report <- result$report
facts <- result$company_facts
html_output <- knitr::is_html_output()

# The two places a company gets its own subsection, so every table can point at them.
overview_tickers <- vapply(result$overviews, function(item) item$ticker, character(1))
earnings_tickers <- vapply(
  purrr::keep(result$earnings_summaries, function(item) !is.na(item$summary)),
  function(item) item$ticker, character(1)
)

link_to <- function(text, anchor) {
  internal_report_link(text, anchor, html_output)
}
# One rule everywhere both appear: the ticker goes to the company's overview, the name
# goes to its earnings write-up. Splitting them means a company that has both is
# reachable in both directions from the same row, and a reader learns one habit rather
# than checking which column is live in which table. Either stays plain text when that
# destination is not in this report, rather than becoming a dead link.
overview_link <- function(ticker) {
  overview_report_link(ticker, overview_tickers, html_output)
}
earnings_link <- function(name, ticker) {
  earnings_report_link(name, ticker, earnings_tickers, html_output)
}
# Sections that predate the split, where the name is still the only column shown.
company_link <- function(name, ticker) {
  if (!length(ticker) || is.na(ticker) || !(ticker %in% overview_tickers)) return(name)
  link_to(name, report_anchor(ticker))
}
# The contents list the report's sections, the strategy brief's own structure, and the
# companies whose earnings are written up. Everything else is marked `.unlisted`, so a
# reader scanning the contents sees the report's shape rather than every category name.
#
# The anchor is written as a heading attribute in HTML and as an inline element in
# Markdown, because neither form works in both: Markdown has no heading attributes, and
# an inline `<a id>` at the start of an HTML heading is read as that heading's text, so
# a listed section arrives in the contents with a blank label.
sub_heading <- function(text, id = NULL, listed = FALSE) {
  report_sub_heading(text, id, listed, html_output)
}
# A saved earnings write-up carries its own "####" headings. Those are structure within
# one company, not report sections, so they are kept out of the contents — otherwise
# "Earnings Call Summary" appears in it once per company.
unlisted_headings <- function(markdown) {
  if (!html_output) return(markdown)
  lines <- strsplit(markdown, "\n", fixed = TRUE)[[1]]
  in_code <- cumsum(grepl("^\\s*```", lines)) %% 2L == 1L
  heading <- grepl("^#{4,6} ", lines) & !in_code
  lines[heading] <- paste0(lines[heading], " {.unlisted}")
  paste(lines, collapse = "\n")
}
fact <- function(ticker, column) {
  value <- facts[[column]][match(ticker, facts$ticker)]
  if (!length(value)) NA else value
}
```

```{r, results='asis'}
# HTML renders the YAML title as its own block; Markdown does not, so the heading is
# added there only. Emitting both is what printed the title twice.
if (html_output) cat(report_table_assets()) else cat("# ", rmarkdown::metadata$title, "\n\n", sep = "")
```

**Report date:** `r report$report_date`

`r report$body`

## Strategy Narrative

```{r, results='asis'}
narrative <- result$strategy_narrative
if (is.null(narrative)) {
  cat("No strategy narrative has been saved. Run `refresh_strategy_narrative()`.\n\n")
} else {
  # The source is a shared-conversation snapshot that does not update itself, so the
  # period it covers is stated here rather than assumed to be current.
  label <- if (is.na(narrative$period)) "period not stated" else paste("week of", narrative$period)
  fetched <- if (is.na(narrative$fetched_at)) "unknown" else substr(narrative$fetched_at, 1, 10)
  cat("*Strategy brief for the ", label, ", retrieved ", fetched, ".*\n\n", sep = "")
  cat(narrative$body, "\n\n", sep = "")
}
```

## Notable Changes

```{r, results='asis'}
if (is.null(result$previous_date)) {
  cat("No earlier final report is available; this report establishes the baseline.\n\n")
} else {
  cat("Price change from ", format(result$previous_date), " to ", format(report$report_date),
      ".\n\n", sep = "")
}
```

```{r, results='asis'}
moves <- result$weekly_moves
if (!is.null(result$previous_date) && nrow(moves)) {
  categories <- dplyr::filter(moves, type == "category") |>
    dplyr::arrange(dplyr::desc(price_move))
  if (nrow(categories)) {
    cat("**Category change, market-cap weighted**\n\n")
    report_table(
      tibble::tibble(Category = categories$name, Change = format_return(categories$price_move)),
      fills = list(Change = categories$price_move),
      sort_values = list(Change = categories$price_move)
    )
  }
}
```

```{r, results='asis'}
stock_moves <- dplyr::filter(moves, type == "stock", !is.na(price_move)) |>
  dplyr::distinct(ticker, name, price_move)
if (!is.null(result$previous_date) && nrow(stock_moves)) {
  shown <- result$movers_shown
  # Direction follows the sign of the move, not the row's position in the ranking:
  # taking the head and tail of a list would label an unchanged company "Declined".
  gained <- dplyr::filter(stock_moves, price_move > 0) |>
    dplyr::arrange(dplyr::desc(price_move)) |>
    utils::head(shown) |>
    dplyr::mutate(Direction = "Gained")
  declined <- dplyr::filter(stock_moves, price_move < 0) |>
    dplyr::arrange(price_move) |>
    utils::head(shown) |>
    dplyr::mutate(Direction = "Declined")
  table <- dplyr::bind_rows(gained, declined)
  if (!nrow(table)) {
    cat("No company price changed since the previous report.\n\n")
  } else {
    cat("**Largest company moves**\n\n")
    report_table(
      tibble::tibble(
        Direction = table$Direction,
        Company = purrr::map2_chr(table$name, table$ticker, company_link),
        Ticker = table$ticker, Change = format_return(table$price_move)
      ),
      fills = list(Change = table$price_move),
      sort_values = list(Change = table$price_move)
    )
  }
}
```

```{r, results='asis'}
if (!nrow(result$changes)) {
  cat("No configured performance changes were identified.\n\n")
} else {
  cat("**Rank and return changes**\n\n")
  for (detail in result$changes$detail) cat("- ", detail, "\n", sep = "")
  cat("\n")
}
```

## Category performance

```{r, results='asis'}
categories <- result$categories
# Each category name drops to its own subsection below, and the heading there comes
# back here. Only categories the report actually lists get a link; the returns table
# can carry a category this report does not break out.
category_link <- function(name) {
  if (!(name %in% report$categories)) return(name)
  link_to(name, category_anchor(name))
}
report_table(
  tibble::tibble(
    Category = purrr::map_chr(categories$category, category_link),
    Companies = categories$company_count,
    `Market cap` = format_market_cap(categories$market_cap),
    `3m Return` = format_return(categories$price_return_3m),
    `12m Return` = format_return(categories$price_return_12m),
    `24m Return` = format_return(categories$price_return_24m)
  ),
  fills = list(
    `3m Return` = categories$price_return_3m,
    `12m Return` = categories$price_return_12m,
    `24m Return` = categories$price_return_24m
  ),
  sort_values = list(
    Companies = categories$company_count,
    `Market cap` = categories$market_cap,
    `3m Return` = categories$price_return_3m,
    `12m Return` = categories$price_return_12m,
    `24m Return` = categories$price_return_24m
  )
)
```

Category returns use the most recently saved market capitalizations as weights.

## Stock performance vs. SPY

One set of companies appears on all three charts: the strongest returns at 3, 12, and
24 months, pooled, plus SPY. The same lines appear on every chart and only the window
changes underneath them, so the charts can be read against each other. Prices are
indexed to 100 at a shared date, so companies with different share prices compare
directly. Any deep-dive selection outside that set is listed beneath each chart with
its return over that window.

```{r}
chart_windows <- c(6L, 12L, 24L)
selections <- lapply(chart_windows, function(months) {
  chart_series(result$price_performance, months, result$chart_stocks, result$chart_candidates)
})
names(selections) <- as.character(chart_windows)
# Built over the drawn set first so those companies take the best-separated slots,
# then everything else, so a company's styling never depends on the chart it is on.
chart_colors <- series_colors(
  c(facts$ticker, "SPY"),
  universe = c(result$chart_stocks, sort(setdiff(facts$ticker, result$chart_stocks)))
)
chart_line_types <- series_line_types(
  c(facts$ticker, "SPY"),
  universe = c(result$chart_stocks, sort(setdiff(facts$ticker, result$chart_stocks)))
)
```

```{r, fig.width=9, fig.height=5.2, results='asis'}
for (months in chart_windows) {
  selection <- selections[[as.character(months)]]
  if (!length(selection$plotted)) {
    cat("No saved price history is available for the selected stocks.\n\n")
    next
  }
  local({
    old_par <- graphics::par(mar = c(3.2, 3.6, 2.4, 0.6), mgp = c(2.2, 0.6, 0))
    on.exit(graphics::par(old_par), add = TRUE)
    plot_indexed_performance(
      result$price_performance, months, selection$plotted, selection$returns,
      title = paste("Last", months, "months"),
      colors = chart_colors, line_types = chart_line_types
    )
  })
  notes <- character()
  if (isTRUE(selection$benchmark_missing)) {
    notes <- c(notes, "SPY has no saved history for this window, so no benchmark line is shown.")
  }
  if (length(selection$undrawn)) {
    notes <- c(notes, paste0(
      "No saved history for this window: ", paste(selection$undrawn, collapse = ", "), "."
    ))
  }
  if (nrow(selection$others)) {
    notes <- c(notes, paste0(
      "Also selected for a deep dive, not charted: ",
      paste0(selection$others$ticker, " ", format_return(selection$others$window_return), collapse = ", "),
      "."
    ))
  }
  if (length(notes)) cat(paste(notes, collapse = " "), "\n\n")
}
```

## Current top stocks

```{r, results='asis'}
for (horizon in return_horizons()) {
  cat(sub_heading(paste("Last", horizon, "Months")))
  table <- result$top_stocks |>
    dplyr::filter(horizon_months == horizon) |>
    dplyr::arrange(overall_rank)
  if (!nrow(table)) {
    cat("No ranked returns are available for this period.\n\n")
    next
  }
  report_table(
    tibble::tibble(
      Rank = table$overall_rank,
      Company = purrr::map2_chr(table$name, table$ticker, earnings_link),
      Ticker = purrr::map_chr(table$ticker, overview_link),
      `Market cap` = format_market_cap(table$market_cap),
      Return = format_return(table$price_return)
    ),
    fills = list(Return = table$price_return),
    sort_values = list(
      Rank = table$overall_rank, `Market cap` = table$market_cap, Return = table$price_return
    )
  )
}
```

## Companies by category

```{r, results='asis'}
category_returns <- result$categories
for (category_name in report$categories) {
  weighted <- category_returns$price_return_3m[match(category_name, category_returns$category)]
  # The label names its own window: the bare percentage beside a category heading
  # read as that category's return over some unstated period.
  label <- paste0("Last 3m: ", format_return(weighted))
  # The name goes back up to the category performance table, so the comparison across
  # categories is one click away from any category being read.
  fill <- NA_character_
  if (html_output && !is.na(weighted)) {
    # The subsector's own return is coloured on the same scale as the categories
    # table, so the heading says how this group compares without a second lookup.
    fill <- return_fills(category_returns$price_return_3m)[
      match(category_name, category_returns$category)
    ]
  }
  heading <- category_report_heading(category_name, label, fill, html_output)
  cat(sub_heading(heading, id = category_anchor(category_name)))
  table <- dplyr::filter(result$stocks, category == category_name)
  if (!nrow(table)) {
    cat("No companies are assigned to this category.\n\n")
    next
  }
  report_table(
    tibble::tibble(
      Company = purrr::map2_chr(table$name, table$ticker, earnings_link),
      Ticker = purrr::map_chr(table$ticker, overview_link),
      `Market cap` = format_market_cap(table$market_cap),
      `3m Return` = format_return(table$price_return_3m),
      `12m Return` = format_return(table$price_return_12m),
      `24m Return` = format_return(table$price_return_24m)
    ),
    fills = list(
      `3m Return` = table$price_return_3m,
      `12m Return` = table$price_return_12m,
      `24m Return` = table$price_return_24m
    ),
    sort_values = list(
      `Market cap` = table$market_cap,
      `3m Return` = table$price_return_3m,
      `12m Return` = table$price_return_12m,
      `24m Return` = table$price_return_24m
    )
  )
}
```

The percentage beside each category is its market-cap-weighted 3-month return. Category
names link back to the category performance table.

## Upcoming earnings

```{r, results='asis'}
upcoming <- result$upcoming_earnings
if (!nrow(upcoming)) {
  cat("No saved earnings dates fall within the next seven days.\n\n")
} else {
  upcoming <- upcoming |>
    dplyr::mutate(
      category = dplyr::coalesce(fact(ticker, "category"), "Uncategorised"),
      market_cap = fact(ticker, "market_cap"),
      return_3m = fact(ticker, "price_return_3m"),
      return_12m = fact(ticker, "price_return_12m")
    )
  for (category_name in unique(upcoming$category[order(-dplyr::coalesce(upcoming$market_cap, -Inf))])) {
    table <- dplyr::filter(upcoming, category == category_name) |>
      dplyr::arrange(dplyr::desc(market_cap))
    cat(sub_heading(category_name))
    report_table(
      tibble::tibble(
        Company = purrr::map2_chr(table$name, table$ticker, earnings_link),
        Ticker = purrr::map_chr(table$ticker, overview_link),
        Date = format(table$next_earnings_date),
        `Market cap` = format_market_cap(table$market_cap),
        `3m Return` = format_return(table$return_3m),
        `12m Return` = format_return(table$return_12m)
      ),
      fills = list(`3m Return` = table$return_3m, `12m Return` = table$return_12m),
      sort_values = list(
        Date = as.numeric(table$next_earnings_date), `Market cap` = table$market_cap,
        `3m Return` = table$return_3m, `12m Return` = table$return_12m
      )
    )
  }
}
```

## Selected earnings highlights

```{r, results='asis'}
if (!length(result$earnings_summaries)) cat("No earnings summaries were selected.\n\n")
for (item in result$earnings_summaries) {
  name <- fact(item$ticker, "name")
  if (is.na(name)) name <- item$ticker
  # Listed in the contents, so the companies written up this week can be reached
  # directly. The heading is the destination other sections link to, so it carries the
  # anchor and no link of its own — a link inside a heading is repeated in the
  # contents, where it reads as a link to somewhere other than the section itself.
  cat(sub_heading(
    sprintf("%s (%s)", name, item$ticker),
    id = earnings_anchor(item$ticker), listed = TRUE
  ))
  cat(
    "*", fact(item$ticker, "category"), " · ", format_market_cap(fact(item$ticker, "market_cap")),
    " · 3m ", format_return(fact(item$ticker, "price_return_3m")),
    " · 12m ", format_return(fact(item$ticker, "price_return_12m")), "*\n\n", sep = ""
  )
  if (is.na(item$summary)) cat(item$message, "\n\n") else {
    cat("**Reported:** ", format(item$report_date), "\n\n",
        unlisted_headings(item$summary), "\n\n", sep = "")
    if (!is.na(item$source_url)) cat("[Google Finance source](", item$source_url, ")\n\n", sep = "")
  }
}
```

## Selected news

```{r, results='asis'}
if (!length(result$news)) cat("No company news was selected.\n\n")
without_news <- character()
for (item in result$news) {
  if (!nrow(item$articles)) {
    without_news <- c(without_news, item$ticker)
    next
  }
  cat(sub_heading(paste0(company_link(item$name, item$ticker), " (", item$ticker, ")")))
  for (index in seq_len(nrow(item$articles))) {
    article_date <- if (is.na(item$articles$published_date[[index]])) {
      paste0("first seen ", item$articles$first_seen_date[[index]])
    } else {
      as.character(item$articles$published_date[[index]])
    }
    cat("- [", item$articles$title[[index]], "](", item$articles$url[[index]], ") — ",
        item$articles$publisher[[index]], ", ", article_date, "\n", sep = "")
  }
  cat("\n")
}
if (length(without_news)) {
  cat("*Companies selected but no news available: ", paste(without_news, collapse = ", "), ".*\n\n", sep = "")
}
```

## Company overviews

```{r, results='asis', fig.width=7, fig.height=2.6}
if (!length(result$overviews)) cat("No company overviews were selected.\n\n")
for (item in result$overviews) {
  cat(sub_heading(
    sprintf("%s (%s)", item$name, item$ticker), id = report_anchor(item$ticker)
  ))
  cat(
    "*", item$category %||% "Uncategorised", " · ", format_market_cap(item$market_cap),
    " · 3m ", format_return(fact(item$ticker, "price_return_3m")),
    " · 12m ", format_return(fact(item$ticker, "price_return_12m")),
    " · 24m ", format_return(fact(item$ticker, "price_return_24m")), "*\n\n", sep = ""
  )
  chart <- performance_chart_data(item$ticker, report$report_date, horizons = 24L)
  if (nrow(chart)) {
    local({
      old_par <- graphics::par(mar = c(2.6, 3.4, 1.2, 0.6), mgp = c(2.1, 0.5, 0))
      on.exit(graphics::par(old_par), add = TRUE)
      plot_indexed_performance(
        chart, 24, unique(chart$ticker), colors = chart_colors
      )
    })
    # A plot in an `asis` chunk is emitted as an image where it is drawn, and an image
    # is inline-level: without a blank line after it the description that follows joins
    # the same paragraph and wraps up the chart's right-hand side. The break is what
    # puts the description below the chart.
    cat("\n\n")
  }
  if (!is.na(item$description) && nzchar(item$description)) cat(item$description, "\n\n")
  if (!is.na(item$provider_description) && nzchar(item$provider_description)) {
    cat(item$provider_description, "\n\n")
  }
}
```

```{r, results='asis'}
# Data coverage and collection warnings are working notes: useful when reviewing a
# draft, noise in the version that gets circulated. They render in the Markdown
# output only.
coverage <- result$coverage
issues <- result$data_issues
recent_listings <- if (is.null(coverage)) NULL else dplyr::filter(coverage, expected_short)
short_history <- if (is.null(coverage)) character() else unexplained_short_history(coverage)
shifted_base <- if (is.null(coverage)) NULL else dplyr::filter(coverage, covers, days_late > 0)
lines <- character()

if (!is.null(issues) && nrow(issues)) {
  lines <- c(lines, paste0("- **", issues$issue, "** — ", issues$subject, ". ", issues$detail))
}
if (length(short_history)) {
  lines <- c(lines, paste0(
    "- Saved history cannot support a ", max(coverage$horizon_months), "-month return for ",
    paste(short_history, collapse = ", "), ". That horizon is blank for them; shorter horizons are unaffected."
  ))
}
if (!is.null(recent_listings) && nrow(recent_listings)) {
  lines <- c(lines, paste0(
    "- Listed less than ", max(coverage$horizon_months), " months ago, so that horizon is blank by nature: ",
    paste0(recent_listings$ticker, " (listed ", format(recent_listings$listed_on), ")", collapse = ", "), "."
  ))
}
if (!is.null(shifted_base) && nrow(shifted_base)) {
  lines <- c(lines, paste0(
    "- Measured from the earliest saved bar rather than the exact window edge, up to ",
    max(shifted_base$days_late), " day(s) later: ", paste(shifted_base$ticker, collapse = ", "), "."
  ))
}
if (!html_output && length(lines)) {
  cat("## Data coverage\n\n")
  cat("Everything below is reported rather than blocking: the report is produced from the data that is available.\n\n")
  cat(paste(lines, collapse = "\n"), "\n\n", sep = "")
}

warnings <- result$scraper_warnings
if (!html_output && isTRUE(result$show_scraper_warnings) && !is.null(warnings) && nrow(warnings)) {
  labels <- c(
    google_earnings = "Google Finance earnings", google_news = "Google Finance news",
    exchange = "Exchange lookup"
  )
  cat("## Data collection warnings\n\n")
  cat("The following Google Finance scrapes did not succeed on their most recent run. ",
      "`fallback` means the article came from the Massive news API instead. ",
      "The report used saved or fallback data where available; check the selectors if this persists.\n\n", sep = "")
  for (index in seq_len(nrow(warnings))) {
    source_label <- labels[[warnings$source[[index]]]] %||% warnings$source[[index]]
    detail <- if (is.na(warnings$detail[[index]])) "" else paste0(" — ", warnings$detail[[index]])
    cat("- **", warnings$ticker[[index]], "** (", source_label, ", ",
        warnings$status[[index]], ", last checked ",
        warnings$checked_at[[index]], ")", detail, "\n", sep = "")
  }
  cat("\n")
}
```

## Methodology

- Returns are split-adjusted price returns for the 3-, 12-, and 24-month periods ending on the report date.
- A return is blank when saved price history does not reach back through its horizon. The provider holds about two years of history from the current date, so on a new cache the 24-month base bar can fall a few days inside the window; a base bar up to `price_base_tolerance_days` late is used rather than blanking the return.
- Chart series are indexed to 100 at one shared date, so lines with different history lengths share an origin. Changes beside each series label are measured over that chart's own window.
- Category returns are market-cap-weighted averages of company returns; raw share prices are not averaged.
- Rankings are calculated independently for each horizon.
- Return colours run green for gains and red for losses, calibrated within each column against the largest absolute move in it. Both arms are matched in lightness, so equal moves in either direction read as equally strong. Green and red are hard to separate with red-green colour blindness, so the signed number in each cell is the channel that always carries the meaning; chart series are labelled at the end of their own lines for the same reason.
- Notable changes compare with the most recent final report at least `previous_report_minimum_days` before this one, whatever weekday it fell on.
- Rendering reads saved local files and makes no external requests.
