---
title: "Healthcare Weekly Monitor"
format:
  html:
    toc: true
    embed-resources: true
params:
  report_path: "inputs/current_report.md"
execute:
  echo: false
  warning: false
  message: false
---

```{r}
source("weekly_report.R")
result <- prepare_report(params$report_path)
report <- result$report
```

# `r report$report_name`

**Report date:** `r report$report_date`

`r report$body`

## Notable changes

```{r, results='asis'}
if (!nrow(result$changes)) cat("No configured performance changes were identified.\n")
for (detail in result$changes$detail) cat("- ", detail, "\n", sep = "")
```

## Category performance

```{r}
category_table <- result$categories |>
  dplyr::transmute(
    Category = category, Companies = company_count,
    `Market cap` = scales::dollar(market_cap, scale = 1e-9, suffix = "B", accuracy = 0.1),
    `3 months` = scales::percent(price_return_3m, accuracy = 0.1), `3m rank` = rank_3m,
    `3m coverage` = scales::percent(market_cap_coverage_3m, accuracy = 1),
    `12 months` = scales::percent(price_return_12m, accuracy = 0.1), `12m rank` = rank_12m,
    `12m coverage` = scales::percent(market_cap_coverage_12m, accuracy = 1),
    `24 months` = scales::percent(price_return_24m, accuracy = 0.1), `24m rank` = rank_24m,
    `24m coverage` = scales::percent(market_cap_coverage_24m, accuracy = 1)
  )
knitr::kable(category_table)
```

Category returns use the most recently saved market capitalizations as weights.

## Current top stocks

```{r, results='asis'}
for (horizon in return_horizons()) {
  cat("### ", horizon, " months\n\n", sep = "")
  table <- result$top_stocks |>
    dplyr::filter(horizon_months == horizon) |>
    dplyr::transmute(Rank = overall_rank, Company = name, Ticker = ticker,
                     Return = scales::percent(price_return, accuracy = 0.1))
  print(knitr::kable(table)); cat("\n\n")
}
```

## Companies by category

```{r, results='asis'}
for (category_name in report$categories) {
  cat("### ", category_name, "\n\n", sep = "")
  table <- result$stocks |>
    dplyr::filter(category == category_name) |>
    dplyr::transmute(
      Company = name, Ticker = ticker,
      `Market cap` = scales::dollar(market_cap, scale = 1e-9, suffix = "B", accuracy = 0.1),
      `3 months` = scales::percent(price_return_3m, accuracy = 0.1), `3m rank` = rank_3m,
      `12 months` = scales::percent(price_return_12m, accuracy = 0.1), `12m rank` = rank_12m,
      `24 months` = scales::percent(price_return_24m, accuracy = 0.1), `24m rank` = rank_24m
    )
  print(knitr::kable(table)); cat("\n\n")
}
```

## Upcoming earnings

```{r}
if (!nrow(result$upcoming_earnings)) {
  cat("No saved earnings dates fall within the next seven days.\n")
} else {
  knitr::kable(dplyr::transmute(
    result$upcoming_earnings, Company = name, Ticker = ticker,
    Date = next_earnings_date, Status = next_date_status
  ))
}
```

## Selected earnings highlights

```{r, results='asis'}
if (!length(result$earnings_summaries)) cat("No earnings summaries were selected.\n")
for (item in result$earnings_summaries) {
  name <- result$companies_input$companies$name[match(item$ticker, result$companies_input$companies$ticker)]
  cat("### ", name, " (", item$ticker, ")\n\n", sep = "")
  if (is.na(item$summary)) cat(item$message, "\n\n") else {
    cat("**Reported:** ", format(item$report_date), "\n\n", item$summary, "\n\n", sep = "")
    if (!is.na(item$source_url)) cat("[Google Finance source](", item$source_url, ")\n\n", sep = "")
  }
}
```

## Selected company overviews

```{r, results='asis'}
if (!length(result$overviews)) cat("No company overviews were selected.\n")
for (item in result$overviews) {
  cat("### ", item$name, " (", item$ticker, ")\n\n", item$description, "\n\n", sep = "")
  if (!is.na(item$provider_description) && nzchar(item$provider_description)) cat(item$provider_description, "\n\n")
}
```

## Selected news

```{r, results='asis'}
if (!length(result$news)) cat("No company news was selected.\n")
for (item in result$news) {
  cat("### ", item$name, " (", item$ticker, ")\n\n", sep = "")
  if (!nrow(item$articles)) cat("No newly saved news was available since the prior final report.\n\n")
  for (index in seq_len(nrow(item$articles))) {
    article_date <- if (is.na(item$articles$published_date[[index]])) {
      paste0("first seen ", item$articles$first_seen_date[[index]])
    } else {
      as.character(item$articles$published_date[[index]])
    }
    cat("- [", item$articles$title[[index]], "](", item$articles$url[[index]], ") — ",
        item$articles$publisher[[index]], ", ", article_date, "\n", sep = "")
  }
  cat("\n")
}
```

```{r, results='asis'}
warnings <- result$scraper_warnings
if (isTRUE(result$show_scraper_warnings) && !is.null(warnings) && nrow(warnings)) {
  labels <- c(google_earnings = "Google Finance earnings", google_news = "Google Finance news")
  cat("## Data collection warnings\n\n")
  cat("The following Google Finance scrapes did not succeed on their most recent run. ",
      "The report used saved or fallback data where available; check the selectors if this persists.\n\n", sep = "")
  for (index in seq_len(nrow(warnings))) {
    source_label <- labels[[warnings$source[[index]]]] %||% warnings$source[[index]]
    detail <- if (is.na(warnings$detail[[index]])) "" else paste0(" — ", warnings$detail[[index]])
    cat("- **", warnings$ticker[[index]], "** (", source_label, ", last checked ",
        warnings$checked_at[[index]], ")", detail, "\n", sep = "")
  }
  cat("\n")
}
```

## Methodology

- Returns are split-adjusted price returns for the 3-, 12-, and 24-month periods ending on the report date.
- Category returns are market-cap-weighted averages of company returns; raw share prices are not averaged.
- Rankings are calculated independently for each horizon.
- Notable changes compare with the latest earlier final report.
- Rendering reads saved local files and makes no external requests.
